---
title: "reveal.js MQ"
subtitle: "A Macquarie University theme for revealjs"
author: "Connor Smith & Thomas Fung"
institute: "School of Mathematical and Physical Sciences"
date: "`r Sys.Date()`"
footer: "[Awesome Quarto & RMarkdown resources for MQ](https://github.com/SmithConnor/revealMQ-presentation)"
format: 
  mq-revealjs:
    width: 1920
    height: 1080
    self-contained: true
---

# Quick Start {.title}

## Headings

### location

Headings are used to define different sections in the revealjs slides:

-   A level 1 heading is used for title slides

-   A level 2 heading is used to indicate individual slides

## highlighting code

### how to


When demonstrating code in a unit, you are able to highlight code incrementally:

```{r}
#| echo: true
#| eval: false
#| code-line-numbers: "1|2"
x <- c(1:5)
y <- sum(x)

```

## Code 1

### animation


Walk your students through code step by step.

```{r}
#| echo: true
#| eval: false
x <- c(1:5)
y <- sum(x)

```

## Code 2

### animation

Walk your students through code step by step.

```{r}
#| echo: true
#| eval: false
x <- c(1:5)
y <- sum(x)
z <- y^2

```

## This is a test slide where I do everything

When you click the **Render** button a presentation will be generated that includes both content and the output of embedded code. [Here](https://www.emilhvitfeldt.com/post/slidecraft-colors-fonts/ "Testing this out") You can embed code like this:

```{r}
1 + 1
```

## Two Column

### Add subtitle here

<hr size="2rem" color="#373A36">

:::: {.columns}

::: {.column width="50%"}
Left column
:::

::: {.column width="50%"}
Right column
:::

::::
